Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-30 Paper/results.tex
Just formatting

\par
To inspect the changes over time for each nation we arrange all the border ASes belonging to a nation into a list. The list of border ASes is reverse sorted
so that the first AS has the highest chokepoint potential. The sum of all these chokepoint potentials is 1.0. Then we step through the list, and record
the cumulative chokepoint potential of all the ASes seen so far. If we plot the number of ASes controled vs the cumulative chokepoint potential for that number
of ASes, we can see how many ASes are required for a certain nation to control different percentages of paths. We repeat this process for each snapshot to highlight
changes over time.

\par
For instance, consider \figurename \ref{fig:multiTime}. 
The x-axis (log-scale, so that countries with large differences in AS counts can be compared more easily) for each plot
is the number of border ASes controlled, and the y-axis is the ratio of in-to-out paths intercepted. Each line represents a different snapshot, with the more red lines being
farther in the past and more blue lines being more recent.

\par
The United States and China are shown here and exhibit some dramatic differences. First, it is worth pointing out that the United States has many more ASes than China, hence
it's line extends further to the right in these plots. We also see that China, in all cases, can control a much larger portion of its paths with much fewer ASes than the
United States. This result is entirely expected. Of more interest is the trends that can be seen over time. The AS-level topology of China's Internet has evolved such that very few
ASes can intercept nearly all BGP paths. The US has evolved in a different way. While it has become somewhat easier for the US to intercept most of its paths, it has become
more difficult to intercept around 70\% of its paths and higher. This suggest an expansion of ASes on the interior and more connections, as well as a strengthening of
the very top ASes.

\par
Not all nations have evolved to a state where it easier to control paths. One example is Germany, as shown in \figurename \ref{fig:multiTime}. For Germany, a fairly constant
trend shows that it has become more difficult to intercept BGP paths. Unlike the other examples, any amount of German border ASes intercept less paths in more recent tests.

\par
In order to compare multiple nations, we have plotted the number of ASes needed to intercept 90\% of in-to-out paths
for each timestamp recorded. These results are detailed in \figurename \ref{fig:nodesFree} and \figurename \ref{fig:nodesCensor}.
The distinct behaviors of each nation are rather striking. We can see a steep decline for some
nations known to limit Internet freedom (China and Turkey) as well as the increase for other nations
(Germany and France). Other nations have stayed more stable. It is worth pointing out that if a nation
has required the same number of border ASes to control many paths over several years, this suggests
that the chokepoints have grown to intercept more paths. The reason for this is that the number of ASes,
and thus the number of paths, has increased globally over time. This fact makes the decline in ASes
needed for some nations even more glaring.

@@

\par
For each timestamp we see what appears to be two general modes of behavior. Nations that are not free or partly free tend to requrie few ASes
to intercept 90\% of their paths. Free nations on the otherhand require varying degrees of large numbers of ASes to control the same portion
of their paths. There are interesting outliers for both situations, however. Countries like Estonia (EE) or Iceland (IS) are very free but require
few border ASes to control most of their paths. The reason for these outliers is likely that their overall AS counts are very low. On the other hand, Russia (RU)
is a very interesting outlier in that it is found to be not free by FOTN, but requires a large number of ASes to control most of its paths. This suggests
that the censorship efforts in Russia might be of types that do not require AS level chokepoints.

>>>>

To inspect the changes over time for each nation we arrange all the border ASes
belonging to a nation into a list. The list of border ASes is reverse sorted so
that the first AS has the highest chokepoint potential. The sum of all these
chokepoint potentials is 1.0. Then we step through the list, and record the
cumulative chokepoint potential of all the ASes seen so far. If we plot the
number of ASes controled vs the cumulative chokepoint potential for that number
of ASes, we can see how many ASes are required for a certain nation to control
different percentages of paths. We repeat this process for each snapshot to
highlight changes over time.

For instance, consider \figurename \ref{fig:multiTime}.  The x-axis (log-scale,
so that countries with large differences in AS counts can be compared more
easily) for each plot is the number of border ASes controlled, and the y-axis
is the ratio of in-to-out paths intercepted. Each line represents a different
snapshot, with the more red lines being farther in the past and more blue lines
being more recent.

The United States and China are shown here and exhibit some dramatic
differences. First, it is worth pointing out that the United States has many
more ASes than China, hence it's line extends further to the right in these
plots. We also see that China, in all cases, can control a much larger portion
of its paths with much fewer ASes than the United States. This result is
entirely expected. Of more interest is the trends that can be seen over time.
The AS-level topology of China's Internet has evolved such that very few ASes
can intercept nearly all BGP paths. The US has evolved in a different way.
While it has become somewhat easier for the US to intercept most of its paths,
it has become more difficult to intercept around 70\% of its paths and higher.
This suggest an expansion of ASes on the interior and more connections, as well
as a strengthening of the very top ASes.

Not all nations have evolved to a state where it easier to control paths. One
example is Germany, as shown in \figurename \ref{fig:multiTime}. For Germany, a
fairly constant trend shows that it has become more difficult to intercept BGP
paths. Unlike the other examples, any amount of German border ASes intercept
less paths in more recent tests.

In order to compare multiple nations, we have plotted the number of ASes needed
to intercept 90\% of in-to-out paths for each timestamp recorded. These results
are detailed in \figurename \ref{fig:nodesFree} and \figurename
\ref{fig:nodesCensor}.  The distinct behaviors of each nation are rather
striking. We can see a steep decline for some nations known to limit Internet
freedom (China and Turkey) as well as the increase for other nations (Germany
and France). Other nations have stayed more stable. It is worth pointing out
that if a nation has required the same number of border ASes to control many
paths over several years, this suggests that the chokepoints have grown to
intercept more paths. The reason for this is that the number of ASes, and thus
the number of paths, has increased globally over time. This fact makes the
decline in ASes needed for some nations even more glaring.

@@

For each timestamp we see what appears to be two general modes of behavior.
Nations that are not free or partly free tend to requrie few ASes to intercept
90\% of their paths. Free nations on the otherhand require varying degrees of
large numbers of ASes to control the same portion of their paths. There are
interesting outliers for both situations, however. Countries like Estonia (EE)
or Iceland (IS) are very free but require few border ASes to control most of
their paths. The reason for these outliers is likely that their overall AS
counts are very low. On the other hand, Russia (RU) is a very interesting
outlier in that it is found to be not free by FOTN, but requires a large number
of ASes to control most of its paths. This suggests that the censorship efforts
in Russia might be of types that do not require AS level chokepoints.
